### 2019-10-16 ch1_introduction/content.tex
update

\begin{itemize}
	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. bioRxiv 079509. 2016 Oct.
	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. Computational methods for trajectory inference from single-cell transcriptomics. European journal of immunology. 2016 Nov;46(11):2496-506.
	\item \textbf{Cannoodt R}, Ruyssinck J, Ramon J, De Preter K, Saeys Y. IncGraph: Incremental graphlet counting for topology optimisation. PloS one. 2018 Apr 26;13(4):e0195997.
	\item Saelens W *, \textbf{Cannoodt R} *, Todorov H, Saeys Y. A comparison of single-cell trajectory inference methods. Nature biotechnology. 2019 May;37(5):547.
	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS: Fast, accurate, and robust single-cell pseudotime. In preparation.
	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyngen: Simulating developing single cells. In preparation.
	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyno: A toolkit for inferring, visualising, and interpreting trajectories. In preparation.
	\item \textbf{Cannoodt R}, Saelens W, Saeys Y, De Preter K. bred: Inferring single cell regulatory networks. In preparation. 
	\item \textbf{Cannoodt R}, Saelens W, Saeys Y. Self-assessment in trajectory inference. In preparation.
\end{itemize}

@@

	\centering\fontsize{9}{11}\selectfont
	\begin{tabularx}{\linewidth}{|p{2cm}llp{1.5cm}X|}
		\hline
		Name & Role & Host & Downloads per year & Description \\ \hline\hline
		\cranpkg{babelwhale} & aut & CRAN & 5810 & Interacting with Docker and Singularity containers \\
		\cranpkg{diffusionMap} & aut & CRAN & 30'450 & Implements diffusion map method of data parameterization, including creation and visualization of diffusion map \\
		\githubpkg{dynverse}{dynbenchmark} & aut & Github & \notavailable & Pipeline for benchmarking trajectory inference methods \\
		\cranpkg{dyndimred} & aut & CRAN & 5535 & Applying dimensionality reduction methods \\
		\githubpkg{dynverse}{dyneval} & aut & Github & \notavailable & Evaluating trajectory inference methods \\
		\githubpkg{dynverse}{dynfeature} & aut & Github & \notavailable & Calculating feature importance scores from trajectories \\
		\githubpkg{dynverse}{dyngen} & aut & Github & \notavailable & Simulating single-cell data using gene regulatory networks \\
		\githubpkg{dynverse}{dynguidelines} & aut & Github & \notavailable & User guidelines for trajectory inference \\
		\githubpkg{dynverse}{dynmethods} & aut & Github & \notavailable & A collection of wrappers for trajectory inference methods \\
		\githubpkg{dynverse}{dyno} & aut & Github & \notavailable & A pipeline for inferring, visualising and interpreting trajectories \\
		\cranpkg{dynparam} & aut & CRAN & 3265 & Creating meta-information for parameters \\
		\githubpkg{dynverse}{dynplot} & aut & Github & \notavailable & A simple visualisation library for trajectories \\
		\githubpkg{dynverse}{dynplot2} & aut & Github & \notavailable & A fully customisable visualisation library for trajectories \\
		\githubpkg{dynverse}{dyntoy} & aut & Github & \notavailable & Generating simple toy data of cellular differentiation \\
		\cranpkg{dynutils} & aut & CRAN & 13'13' & Common functionality for the dynverse packages \\
		\cranpkg{dynwrap} & aut & CRAN & 990 & A common format for trajectories \\
		\cranpkg{GillespieSSA} & aut & CRAN & 7880 & Gillespie's Stochastic Simulation Algorithm (SSA) \\
		\cranpkg{GillespieSSA2} & aut & CRAN & 4950 & Gillespie's Stochastic Simulation Algorithm for Impatient People \\
		\githubpkg{dynverse}{gng} & aut & Github & \notavailable & An Rcpp implementation of the Growing Neural Gas algorithm \\
		\cranpkg{incgraph} & aut & CRAN & 3565 & Incremental graphlet counting for network optimisation \\
		\cranpkg{lmds} & aut & CRAN & 815 & Landmark Multi-Dimensional Scaling \\
		\cranpkg{princurve} & aut & CRAN & 29'100 & Fits a principal curve in arbitrary dimension \\
		\cranpkg{proxyC} & aut & CRAN & 117'480 & Computes proximity in large sparse matrices \\
		\cranpkg{qsub} & aut & CRAN & 3585 & Running commands remotely on gridengine clusters \\
		\cranpkg{SCORPIUS} & aut & CRAN & 4520 & Inferring developmental chronologies from single-cell RNA sequencing data \\ \hline\hline

>>>>

\begin{itemize}
	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. bioRxiv 079509. 2016 Oct.
	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. Computational methods for trajectory inference from single-cell transcriptomics. European journal of immunology. 2016 Nov;46(11):2496-506.
	\item \textbf{Cannoodt R}, Ruyssinck J, Ramon J, De Preter K, Saeys Y. IncGraph: Incremental graphlet counting for topology optimisation. PloS one. 2018 Apr 26;13(4):e0195997.
	\item Saelens W *, \textbf{Cannoodt R} *, Todorov H, Saeys Y. A comparison of single-cell trajectory inference methods. Nature biotechnology. 2019 May;37(5):547.
%	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS: Fast, accurate, and robust single-cell pseudotime. In preparation.
%	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyngen: Simulating developing single cells. In preparation.
%	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyno: A toolkit for inferring, visualising, and interpreting trajectories. In preparation.
%	\item \textbf{Cannoodt R}, Saeys Y, De Preter K. bred: Inferring single cell regulatory networks. In preparation. 
%	\item \textbf{Cannoodt R}. Self-assessment in trajectory inference. In preparation.
\end{itemize}

@@

	\centering\fontsize{9}{11}\selectfont
	\begin{tabularx}{\linewidth}{|p{2cm}llp{1.5cm}X|}
		\hline
		Name & Role & Host & Downloads per year & Description \\ \hline\hline
		\cranpkg{babelwhale} & aut & CRAN & 5810 & Interacting with Docker and Singularity containers \\
		\cranpkg{diffusionMap} & aut & CRAN & 30'450 & Implements diffusion map method of data parameterization, including creation and visualization of diffusion map \\
		\githubpkg{dynverse}{dynbenchmark} & aut & Github & \notavailable & Pipeline for benchmarking trajectory inference methods \\
		\cranpkg{dyndimred} & aut & CRAN & 5535 & Applying dimensionality reduction methods \\
		\githubpkg{dynverse}{dyneval} & aut & Github & \notavailable & Evaluating trajectory inference methods \\
		\githubpkg{dynverse}{dynfeature} & aut & Github & \notavailable & Calculating feature importance scores from trajectories \\
		\githubpkg{dynverse}{dyngen} & aut & Github & \notavailable & Simulating single-cell data using gene regulatory networks \\
		\githubpkg{dynverse}{dynguidelines} & aut & Github & \notavailable & User guidelines for trajectory inference \\
		\githubpkg{dynverse}{dynmethods} & aut & Github & \notavailable & A collection of wrappers for trajectory inference methods \\
		\githubpkg{dynverse}{dyno} & aut & Github & \notavailable & A pipeline for inferring, visualising and interpreting trajectories \\
		\cranpkg{dynparam} & aut & CRAN & 3265 & Creating meta-information for parameters \\
		\githubpkg{dynverse}{dynplot} & aut & Github & \notavailable & A simple visualisation library for trajectories \\
		\githubpkg{dynverse}{dynplot2} & aut & Github & \notavailable & A fully customisable visualisation library for trajectories \\
		\githubpkg{dynverse}{dyntoy} & aut & Github & \notavailable & Generating simple toy data of cellular differentiation \\
		\cranpkg{dynutils} & aut & CRAN & 13'130 & Common functionality for the dynverse packages \\
		\cranpkg{dynwrap} & aut & CRAN & 990 & A common format for trajectories \\
		\cranpkg{GillespieSSA} & aut & CRAN & 7880 & Gillespie's Stochastic Simulation Algorithm (SSA) \\
		\cranpkg{GillespieSSA2} & aut & CRAN & 4950 & Gillespie's Stochastic Simulation Algorithm for Impatient People \\
		\githubpkg{dynverse}{gng} & aut & Github & \notavailable & An Rcpp implementation of the Growing Neural Gas algorithm \\
		\cranpkg{incgraph} & aut & CRAN & 3565 & Incremental graphlet counting for network optimisation \\
		\cranpkg{lmds} & aut & CRAN & 815 & Landmark Multi-Dimensional Scaling \\
		\cranpkg{princurve} & aut & CRAN & 29'100 & Fits a principal curve in arbitrary dimension \\
		\cranpkg{proxyC} & aut & CRAN & 117'480 & Computes proximity in large sparse matrices \\
		\cranpkg{qsub} & aut & CRAN & 3585 & Running commands remotely on gridengine clusters \\
		\cranpkg{SCORPIUS} & aut & CRAN & 4520 & Inferring developmental chronologies from single-cell RNA sequencing data \\ \hline\hline
